Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-29 paper/paper.Rmd
fix blockCV name in header
fix author display in header

---
documentclass: jss
author:
  - name: Patrick Schratz
    affiliation: 'Friedrich-Schiller-University Jena'
    # affiliaton2: 'Ludwig-Maximilians-University Munich'
    # use this syntax to add text on several lines
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{patrick.schratz@uni-jena.de}
  - name: Alexander Brenning
    affiliation: 'Friedrich Schiller University Jena'
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{alexander.brenning@uni-jena.de}
  - name: Marc Becker
    affiliation: 'Ludwig-Maximilians-University Munich \AND'
    address: |
      Department of Statistics
      Statistical Learning and Data Science group
    # To add another line, use \AND at the end of the previous one as above
  - name: Michel Lang
    affiliation: TU Dortmund University
    address: |
      | Faculty of Statistics
title:
  formatted: "\\pkg{mlr3spatiotempcv}: Spatiotemporal resampling methods for \\pkg{mlr3}"
  # If you use tex in the formatted title, also supply version without
  plain:     "mlr3spatiotempcv: spatiotemporal resampling methods for mlr3"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The R package [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is an extension package of the machine learning framework [mlr3](https://mlr3.mlr-org.com) [@mlr3].
  It adds support for spatiotemporal resampling methods and respective visualization methods.
  Spatiotemporal resampling methods are needed to account for the existence of different autocorrelation types (spatial autocorrelation (SAC), temporal autocorrelation (TAC) or spatiotemporal autocorrelation (STAC)) in datasets.
  These autocorrelation types cause biased performance estimates of varying magnitude in cross-validation when ignored.
  At the time of writing, various R packages implementing different spatiotemporal partitioning strategies exist: CAST [@cast], blockCV [@blockCV] or sperrorest [@brenning2012].
  There are some resampling methods used in scientific studies for which the source code is either not available or a different programming language has been used [@roberts2017; @pohjankukka2017]

@@

#### Spatial buffering --- \pkg{blockCV}

>>>>

---
documentclass: jss
author:
  - name: Patrick Schratz
    affiliation: 'Friedrich-Schiller-University Jena'
    # affiliaton2: 'Ludwig-Maximilians-University Munich'
    # use this syntax to add text on several lines
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{patrick.schratz@uni-jena.de}
  - name: Alexander Brenning
    affiliation: 'Friedrich Schiller University Jena \AND'
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{alexander.brenning@uni-jena.de}
  - name: Marc Becker
    affiliation: 'Ludwig-Maximilians-University Munich'
    address: |
      Department of Statistics
      Statistical Learning and Data Science group
    # To add another line, use \AND at the end of the previous one as above
  - name: Michel Lang
    affiliation: TU Dortmund University
    address: |
      | Faculty of Statistics
title:
  formatted: "\\pkg{mlr3spatiotempcv}: Spatiotemporal resampling methods for \\pkg{mlr3}"
  # If you use tex in the formatted title, also supply version without
  plain:     "mlr3spatiotempcv: spatiotemporal resampling methods for mlr3"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  The R package [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is an extension package of the machine learning framework [mlr3](https://mlr3.mlr-org.com) [@mlr3].
  It adds support for spatiotemporal resampling methods and respective visualization methods.
  Spatiotemporal resampling methods are needed to account for the existence of different autocorrelation types (spatial autocorrelation (SAC), temporal autocorrelation (TAC) or spatiotemporal autocorrelation (STAC)) in datasets.
  These autocorrelation types cause biased performance estimates of varying magnitude in cross-validation when ignored.
  At the time of writing, various R packages implementing different spatiotemporal partitioning strategies exist: CAST [@cast], blockCV [@blockCV] or sperrorest [@brenning2012].
  There are some resampling methods used in scientific studies for which the source code is either not available or a different programming language has been used [@roberts2017; @pohjankukka2017]

@@

#### Spatial buffering --- blockCV
